State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-29 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
repaired typos

where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an i.i.d. disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{s}-\mathbf{r}))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{s}-\mathbf{r})$~\cite{Rasmussen2005}. This term is added to account for uncertainty in the model. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper. The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function 

@@

	\mathbf{x}_{t+1} = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t +\mathbf{e}_t.

@@

This reduced model can be manipulated into a standard state-space model in the form (see \ref{Simplifying Decomposition})
\begin{eqnarray}
	\label{Homogeneous SS Model} \mathbf{x}_{t+1} &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t + \mathbf{e}_t \\
	&=& Q\left(\mathbf{x}_t\right) + \mathbf{e}_t 
\end{eqnarray}
where
\begin{eqnarray}
Q\left( \mathbf{x}_t \right) &=& q(\mathbf{x}_t)\boldsymbol{\theta} - \xi\mathbf{x}_t \label{eq:QmatrixForSigmapoints}\\
	\mathbf{e}_t &=& \label{eq:Reducednoiseterm} \boldsymbol{\Gamma}^{-1}\int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}, \\
	\boldsymbol{\Gamma} &=& \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)d\mathbf{r}}, \label{DefGamma} 
\end{eqnarray}

@@

The finite state space model given in \ref{eq:ReducedForm} is linear with respect to parameters. Therefore a least square (LS) method can be applied to estimate the unknown parameters. We define $L \times n_{\theta}$ matrix

@@

	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta}

@@

Given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write

@@

	\right],\quad \boldsymbol \xi=\left[

>>>>

where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an i.i.d. disturbance such that $e_t\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a spatial Gaussian Process with mean zero and covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}. This term is added to account for uncertainty in the model. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper. The mapping between the membrane voltage and the collected iEEG/LFP data is modelled using the observation function 

@@

	\mathbf{x}_{t+1} = Q(\mathbf{x}_t) +\mathbf{e}_t.

@@

\begin{equation}\label{eq:QmatrixForSigmapoints}
	Q(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta} + \xi\mathbf{x}_t.

@@

The finite state space model given in \ref{eq:ReducedForm} is linear with respect to parameters. Therefore a least square (LS) method can be applied to estimate the unknown parameters. The create the least squares parameter estimator we first define the $L \times n_{\theta}$ matrix

@@

	\mathbf{q}(\mathbf{x}_t) = \int_\Omega \boldsymbol{\Psi}(\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) d\mathbf{r}' \boldsymbol{\theta}.

@@

Now given a state estimate sequence from the unscented Rauch Tung Striebel smoother (URTSS), we can write

@@

	\right],\quad \mathbf{e}=\left[
